\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-10 paper/main.tex
.

Both approaches may be used in conjunction with network inference
\cite{}.

>>>>

Both approaches may be used in conjunction with network inference
\cite{}. Biological networks used for DTI prediction include
protein--protein interaction networks \cite{} and networks including
several other types of biological relations, including similarity
between represented entities \cite{PREDICT}. Network-based DTI
prediction methods use the guilt-by-association principle
\cite{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1002444}
and assume that a protein is a likely target for a drug if many of the
protein's neighbors in the interaction network are targets of the drug
\cite{https://academic.oup.com/bioinformatics/article/32/7/1057/1743938,
  others}. Network-based methods have been applied successfully
to DTI prediction. However, if DTIs are taken as direct physical
interactions between a drug and protein, it remains an unresolved
question whether the network-based guilt-by-association hypothesis is
true, or whether an interaction of a drug and protein dys-regulates
several of the protein's interaction partners, and therefore resulting
in downstream effects that are not direct interactions but only
downstream consequences of an interaction.
